\documentclass[a4paper,11pt]{article}

\usepackage{amsfonts,amsthm}
\usepackage[pdftex]{graphicx}
\usepackage[svgnames]{xcolor}
\usepackage[top=2.5cm,left=2.5cm,right=2.5cm,bottom=2.5cm]{geometry}
  \textheight=700px

\usepackage{multicol}

% Accents %
\usepackage{url}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{enumitem}

\frenchspacing
\pagestyle{empty}
\setlist[itemize]{leftmargin=*}

\newcommand{\breakvspace}[1]{\pagebreak[2]\vspace{#1}\pagebreak[2]}
\newcommand{\nobreakvspace}[1]{\nopagebreak[4]\vspace{#1}\nopagebreak[4]}
\newcommand{\spacedhrule}[2]{\breakvspace{#1}\hrule\nobreakvspace{#2}}
\newcommand{\maintitle}[1]{\noindent{\LARGE \textbf{#1}}}

\begin{document}


\maintitle{Clément Hussenot-Desenonges | Curriculum Vitae}

\spacedhrule{0.5em}{-0.4em}

\section*{}
  \begin{itemize}
    \item[]
    A passionate technophile, I worked for several Startups \& Large Companies including Veepee, D2SI, Praditus, af83, Accenture and SQLI, communication agencies including Mazarine Digital and La Chose, and was the founder of an interactive communication agency from 2005 to 2012 (Emeth Animation). As a net result, I bring all-round capability within Software \& Operation Management, as well as the ability to identify and implement improvement to enhance productivity or engage teams. 
    \item[]
    HUSSENOT-DESENONGES Clément, Marie, Coton
    - Nationality: French - Age: 42 \\ cell; 0033 (0) 6167 72183 -
    chussenot@gmail.com - 11 rue des Sablons, Paris 75116.
    
\spacedhrule{0.5em}{-0.4em}

\section*{Core Skills}
  \begin{minipage}[t]{0.29\textwidth}
    \subsection*{Management}
    IT Operations Management (ITOM), Communication, 
    Financial control, Large Scale Project Management, Change \& Persuasion, Address Adhesion,
    Performance Management, Staff Recruitment/Training
  \end{minipage}
  \hspace{0.035\textwidth}
  \vrule
  \hspace{0.035\textwidth}
  \begin{minipage}[t]{0.28\textwidth}
    \subsection*{Tech}
    Shell, Containers \\
    Git, Vim, Tmux\\
    Unix \& BSD systems\\
    Markdown, TDD, CI, CD\\
    Agile (SAFe, XP) \\
    Cloud (AWS, GCP) \\
  \end{minipage}
  \hspace{0.035\textwidth}
  \vrule
  \hspace{0.035\textwidth}
  \begin{minipage}[t]{0.28\textwidth}
    \subsection*{Languages}
    \textbf{French} (native)\\
    \textbf{English} (fluent)\\
    \textbf{Italian} (notions)
  \end{minipage}


\spacedhrule{1.5em}{-0.4em}

\section*{Career Summary}

  \begin{itemize}
    \item[--]
      \textbf{Platform Engineering Manager} – ManoMano - March 2019 - Present\\
      \textit{ManoMano today faces the challenges of a rapidly changing competitive landscape, evolving security requirements, and performance scalability. As a manager I help with my team (7) the growth of ManoMano with this main mission:
        Monitor key business and systems metrics, Provide Tooling to help understand and debug our systems in production, Avoid web performance drift and improving it instead, Control the expenses associated with Cloud resources, Provide the framework for rapid and efficient management of incidents, Experiment in production to minimize failures blast radius. We maintain 3 technical products and the observability platform. My mission is to reduce the risk of production downtime, Cloud budgets misuse or web performance degradation. I have proposed innovative solutions and organised 3 chaos engineering events with 100 people in the first edition. Firstly Site Reliability Engineer, I worked on the migration of the outsourced ManoMano Platform to Amazon Web Services (AWS), and then the construction of the current Platform.} 
    \item[--]
      \textbf{Lead Site Reliability Engineer} - Veepee - July 2018 - March 2019 \\
      \textit{The Veepee group brings together different European brands, consisting of 6,000 employees. A multi-specialist online shop with distinct universes for fashion, home, travel, sport, beauty, children, food and entertainment. At Veepee, as Lead Site Reliability Engineer, I was in charge of a team (5) for the following product domains, B2B, BI, Data-science, Human Resources. We was in charge of building infrastructures and services, server administration and incident management on numerous Veepee applications. I had to lead the project of a common Platform for the whole Tech.}
    \item[--]
      \textbf{Cloud \& Automation Consultant} - D2SI - January 2017 - June 2018 \\
      D2SI (renamed DevoTeam Revolve) is an IT consulting firm specialised in Automation and more specifically in Devops strategy, public cloud, continuous integration, deployment and continuous delivery of applications. As a consultant at D2SI, I have worked for many clients, including Veolia, Renault \& Renault Digital, Neovia. Lead Ops on the Renault Digital account, I worked on the constitution of a technical team (12) in charge of IT operations by managing a massive migration of the group's applications on AWS pushed by over 500 engineers.}
    \item[--]
      \textbf{Chief Technical Officer} - Praditus - June 2014 - September 2016 \\
      Praditus is a solution for HR professionals based on advanced psychometrics. As CTO at Praditus, I was responsible for the product roadmap, platform architecture and security, managing a technical team (5). The technical stack, Ruby, Elixir, ClojureScript being deployed via some CI pipelines to a container orchestrator on AWS (ECR).}
    \item[--]
      \textbf{Presales \& Senior Developer} - af83 - May 2012 - March 2014 \\
      \textit{af83 was a famous innovation agency with offices in Paris and San Francisco, specialising in experience design, technology and digital strategy. I worked closely with project teams \& sales.}
      \textit{Clients: Europe 1, Mon Album Photo, SFR, ADAGP, CISAC, Ijenko, Suez, Chopard}
    \item[--]
      \textbf{CEO - Owner} - Emeth Animation - December 2005 - February 2012 \\
      \textit{Clients: Areva, General Electric, LVMH, Axa, Generali}
    \item[--]
      \textbf{Freelance Web Developer} December 2002 - November 2005 \\
      \textit{Accenture, SQLI, Mazarine Digital, La Chose}
    \item[--]
      \textbf{Motion Designer \& Web Developer} - Abaque Micro - September 2000 - November 2002 \\
      \textit{}
  \end{itemize}


\spacedhrule{0.5em}{-0.4em}

\section*{Education \& Qualifications}

\begin{itemize}
  \item[--] \textbf{Assistant Réalisateur Multimedia}, Paris - CFT Gobelins (1999-2000)
  \item[--] \textbf{Arts plastiques}, Université Paris Nord (1998)
  \item[--] \textbf{BAC S}, La Rochelle - Lycée Dautet (1997)
\end{itemize}

\spacedhrule{0.5em}{-0.4em}

\end{document}

